A Realistic Guide to Making Data Available Alongside Code to Improve Reproducibility.

### 2020-08-25 new-paper.Rmd
read table image

```{r incentable-table, fig.cap = "Table of the mechanism for behavior change, the incentive, and our assessment of where the elements of Data, Code, and Computational Environment rank in terms of completing these aspects. We note that Data is often required, but the preceding steps are not required. This is in contrast to Code having no policy"}
library(gt)
incentive_table <- tibble(
  Mechanism = c("Policy", "Incentives", "Communities", "UI/UX", "Infrastructure"),
  Incentive = c("Required", "Rewarding", "Normative", "Easy", "Possible"),
  Data = c(100, 0, 0, 0, 100),
  Code = c(0, rep(100, 4)),
  `Computational Environment` = c(0, 0, 0, 50, 100)
  )

incentive_table %>%
  gt() %>%
  data_color(
    columns = vars(Data, Code, `Computational Environment`),
    colors = scales::col_numeric(
      # Using a function from paletteer to generate a vector of colors
      # Note that you need to wrap paletteer_d outputs in as.character()
      palette = colorspace::sequential_hcl(n = 3, palette = "Greens2", rev = TRUE),
      # Domain is from scales::col_numeric
      # Domain = The possible values that can be mapped
      # We don't HAVE to set a range for this since
      # we're using it inside data_color()
      domain = NULL
    )
  ) %>%
  gtsave("figures/gt-incentive-table.png")

# knitr::include_graphics("figures/gt-incentive-table.png")
```

>>>>

```{r incentable-table, fig.cap = "Table of the mechanism for behavior change, the incentive, and our assessment of where the elements of Data, Code, and Computational Environment rank in terms of completing these aspects. We note that Data is often required, but the preceding steps are not required. This is in contrast to Code having no policy"}
knitr::include_graphics("figures/gt-incentive-table.png")
```
